A Fredholm integral equation approach to computing Stokes eigenvalues in the plane

### 2019-03-24 doc/draft-01-stokes/03analysis.tex
Updating paper

Let $\Omega$ be a bounded domain with $C^2$ boundary
denoted by $\Gamma$.
The Dirichlet boundary problem specifies the
velocity of the fluid on the boundary, i.e.

@@

\begin{thrm}
The oscillatory Stokeslet, as defined in \eqref{eq:ostokeslet}, 
satisfies the radiation condition in Definition \ref{def:radcond}.
Suppose that $\Gamma$ is the boundary of a region $\Omega$
and is $C^{2}$. 
Suppose that $\bmu \in C(\Gamma)$ and satsifies
$\int_{\Gamma} \bmu \cdot \bnu dS = 0$, where
$\bnu$ dentoes the outward normal to the curve $\Gamma$.
Then, the oscillatory Stokes 
double layer potential $\bD[\bmu]$, as defined in \eqref{eq:doublelayer},
also satisfies the radiation condition.
\end{thrm}

\begin{proof}
Consider the Stokeslet induced by an arbitrary charge
$k^2 \bpsi$ at the origin where $\psi \in \mathbb{C}^2$ 
is a constant. Let $r = |\xx|$,
$\bnu(\xx) = \xx/|\xx|$, and $\btau(\xx) = \bnu(\xx)^\perp$. We have

@@

\begin{equation}
\left | \nabla \left( \partial_{\tau_x} \left ( 
\nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bpsi  \right )
\right) \right | = 0 \; , \nonumber
\end{equation}
so that the Stokeslet satisfies the radiation condition.

For the double layer potential, we only establish the
decay of the pressure, which we will denote by $p^\bD$;
the rest of the terms in \eqref{eq:radcond} can be bounded
using an argument like that for the Stokeslet above.
Because $p^\bD$ is harmonic in the exterior of any disc
containing $\Gamma$, it is sufficient to show that
$|\nabla p^\bD| = \bigo (1/r^2)$. Let $\btau$ denote the
positively oriented tangent to the curve $\Gamma$ and
$\mu_\nu(\yy)$ and $\mu_\tau(\yy)$ denote $\bmu(\yy) \cdot \bnu(\yy)$ and
$\bmu(\yy) \cdot \btau(\yy)$, respectively. Substituting
$\bD \bmu$ into \eqref{eq:ostokes}, we obtain

@@

\note{Manas: check out new argument below.}

@@

\begin{proof}
Since $\bu$ satisfies the radiation condition at $\infty$ and $\bt = i\eta \bu$
on $\Gamma$, it follows from~\cref{eq:repinfest} that
\begin{align*}
0 &=
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
dV \nonumber \\
& \qquad - 2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\bt} dS  \right) \\
&= 
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
dV \nonumber \\
& \qquad + 2 \left( \left (\Re(k)\Re(\eta) + \Re(k)\Re(\eta)
\right ) \int_{\Gamma} |\bu|^{2} dS  \right)
\, .
\end{align*}
Because all of the quantities in the last expression above are
nonnegative, we have that
\begin{equation}
  \int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \, .
  \nonumber
\end{equation}
The result then follows from the uniqueness of solutions to the exterior
Dirichlet problem.
\end{proof}

@@

\subsubsection{Dirichlet eigenvalues --- double layer
  representation}
\label{subsec:dlanalysis}
Suppose that the solution to the oscillatory
Stokes Dirichlet problem, \cref{eq:dir_interior},
is represented using a double layer potential defined
on $\Gamma$, i.e. setting $\bu = \bD_{k} \bmu$ for
an unknown density $\bmu$. 
Substituting this expression
into the boundary condition and applying
\cref{lem:jump-conds}, we obtain

@@

On simply connected domains, there is a one-to-one correspondance between
the eigenvalues of the Dirichlet problem for
the Stokes equation
and the values of $k$ for which the operator $(\cI - 2\cD_{k} - 2\cW)$
is not invertible. To prove this, we require the results
above and the following lemma:
\begin{lem}
  \label{lem:nutracli}
  If $\bt^{-}$ is the surface traction associated
  with an interior Dirichlet Stokes eigenfunction $\bu$,
  then $\bt^{-}$ and $\bnu$ are linearly independent.
\end{lem}
\begin{proof}
We first note that $\bS_{k}[\bnu](\bx) = 0$ for all $\bx \in \Omega$.
This follows from the application of the divergence theorem and the fact that
oscillatory Stokeslet is divergence free in $\Omega$. 
If $\bt^{-}$ is a surface traction associated with a Stokes eigenvalue, then
using Green's theorem, it follows that
$\bS_{k}[\bt^{-}](\bx) = \bu(\bx) \neq 0$ for $\bx \in \Omega$ and
thus $\bt^{-}$ and $\bnu$ are linearly independent.
\end{proof}

We now have

\begin{thrm}
\label{thm:dlmain}
Suppose that $\Omega$ is a bounded, simply connected domain. Then, the operator
$(\cI - 2\cD_{k} - 2 \cW)$ is not invertible if and only if $k^2$ is a
Dirichlet eigenvalue for the Stokes equation on $\Omega$.
\end{thrm}
\begin{proof}
  Suppose that $k^2$ is not a Dirichlet eigenvalue for
  the Stokes equation on
$\Omega$. 
Suppose further that $\bmu$ satisfies
\begin{equation}
(\cI - 2\cD_{k} - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
\end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:dlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:dlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu]$ in $\Omega$.
Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
and applying~\cref{lem:jump-conds}, we get that the interior
limit of the velocity $\bu^{-}$, is given by $(\cI - 2\cD_{k}) \bmu = 0$
on $\Gamma$. Since $k^2$ is not a Dirichlet eigenvalue for the Stokes
equation on $\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
In particular, this implies that the interior limit of the surface traction
denoted by $\bt^{-} = 0$ on $\Gamma$. 
Using~\cref{lem:jump-conds} again, we conclude that the exterior limit
of the surface traction, $\bt^{+}$, is $0$ on $\Gamma$. 
Note that $\bu$ is a radiating solution of the oscillatory
Stokes equation in the exterior $E$, as $\cW[\mu] = 0$ implies
$\int_{\Gamma} \bmu \cdot \bnu = 0$.
From the uniqueness of the Neumann problem in the
exterior $E$, we conclude that $\bu \equiv 0$ in $E$ as well,
which in particular implies that
the exterior limit of the velocity, $\bu^{+}$, is $0$ on $\Gamma$.   
Using the jump conditions in~\cref{lem:jump-conds} again, we
get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$.
Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k^2$
is not a Dirichlet eigenvalue for the Stokes equation on $\Omega$.

@@

\begin{proof}
  Suppose that $k^2$ is not a Dirichlet eigenvalue for the
  Stokes equation on $\Omega$. Suppose further that $\bmu$ satisfies
  \begin{equation}
    (\cI - 2\cD_{k} -2i\eta\cS_{k} - 2\cW) \bmu = 0 \, ,
    \label{eq:mlproofrep}
  \end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2i\eta \cS_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:mlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2i\eta\cS_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:mlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k} - 2i\eta \cS_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu] -2i\eta\bS_{k}[\bmu]$
in $\Omega$. Then $\bu$ is a solution to the oscillatory
Stokes equation in $\Omega$, and applying~\cref{lem:jump-conds},
we get that the interior limit of the velocity
$\bu^{-} = (\cI - 2\cD_{k} -2i\eta\cS_{k}) \bmu = 0$ on $\Gamma$.
Since $k^2$ is not a Dirichlet eigenvalue for the Stokes equation
on $\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
This in particular implies that the interior limit of the
surface traction, denoted by $\bt^{-}$, is $0$ on $\Gamma$.
Using~\cref{lem:jump-conds} we observe that $\bt^{+}
= i\eta \bmu(\xx)$ and $\bu^{+} = \bmu(\xx)$ on $\Gamma$.
\begin{remark}
  Note that there is potential for confusion here
  in that the exterior limit with respect to $\Omega$ 
  for the boundary $\Gamma_{j}$ is the traditional interior 
  limit with respect to the obstacle region $\Omega_{j}$.
\end{remark}
We first show that $\bmu=0$ on $\Gamma_{0}$. 
To this end, note that $\bu$ is a radiating solution
of the oscillatory Stokes equation in the exterior $E$,
since $\cW[\bmu] = 0$ implies that $\int_{\Gamma} \bmu
\cdot \bnu = 0$. From the uniqueness of the impedance problem
in the exterior $E_0$ of $\Omega_0$, we conclude that
$\bu \equiv 0$ in $E_0$ as well, which in particular
implies that $\bu^{+}=0$ on $\Gamma_{0}$.   
Using the jump conditions in~\cref{lem:jump-conds}
again, we get that
$\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$ on
$\Gamma_{0}$. To show that $\bmu=0$ on
$\Gamma_{j}$, we observe that $\bu$ is also a
solution to the oscillatory Stokes equation in each
of the obstacles $\Omega_{j}$.
Applying the energy-type identity \cref{eq:greenlike}
and using the fact that 
the interior limits with respect to $\Omega_{j}$
of the surface traction and the velocity
are $i\eta \bmu$ and $\bmu$ respectively, we get
\begin{equation}
\int_{\Omega_{j}} (|e(\bu)|^{2} - \overline{k}^{2} |\bu|^2) dV 
= \int_{\Gamma_{j}} \bu \cdot \overline{\bt} dS = 
i\overline{\eta}\int_{\Gamma_{j}} |\bmu|^2 dS \, .
\end{equation}
Taking the imaginary part of the above equation,
we get
\begin{equation}
2 \text{Re}(k) \text{Im}(k) \int_{\Omega_{j}} |\bu|^2 + \text{Re}(\eta)
\int_{\Gamma_{j}} |\bmu|^2 dS = 0 \, .
\end{equation}
Since $\text{Re}(\eta)>0$, this implies that
$\bmu=0$ for $\xx \in \Gamma_{j}$, $j=1,2,\ldots m$. 
Thus, $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is
invertible when $k^2$ is not a Dirichlet eigenvalue
for the Stokes equation on $\Omega$.

From \cref{thrm:rep-theorem}, we have 
\begin{equation} \label{eq:rep-theorem}
  \bS [\bt](\xx) - \bD[\bu](\xx) = \begin{cases} 
    \bu(\xx) &\quad \xx \in \Omega \, , \\
    0 &\quad \xx \in \Omega^{C} \; .
    \end{cases}
  \end{equation}
Suppose that $k^2$ is Dirichlet eigenvalue for
the Stokes equation on $\Omega$ and let $\bu$
denote the corresponding eigenfunction and $\bt$ denote
its surface traction. Note that \cref{thrm:rep-theorem}
implies that $\cS_{k}[\bt^{-}] = 0$, since
$\bu^{-}=0$ on $\Gamma$. Applying \cref{thrm:rep-theorem}
to the pair $\bt^{-}, \bu^{-}$ and evaluating the
traction on $\Gamma$ using~\cref{lem:jump-conds},
we get
\begin{equation}
\bt^{-} = (\cDt_{k} + \frac{1}{2} \cI) \bt^{-} \, . 
\end{equation}
Combining these two identities, we get
that
\begin{equation}
(-\cI - 2\cD_{k} -2i\eta \cS_{k}) \bt^{-} = 0 \, .
\end{equation}
As in the proof of~\cref{thm:dlmain}, letting
$c = \left< \bt^{-} ,\bnu \right>$, it follows that
\begin{equation}
  (-\cI - 2\cD_{k} - 2i \eta \cS_{k} - 2\cW)
  (\bt^{-} - c\bnu) = 0 \, ,
\end{equation}
where $\bt^{-} - c\bnu \neq 0$.
Since $\bt^{-} - c\bnu$ is non-trivial and both
$i\eta \cS_{k}$ and $\cW$ are self-adjoint with respect
to the bilinear form \cref{eq:bi_form},
it follows from the Fredholm alternative
that the operator $\cI - 2\cDk -2i\eta \cSk - 2\cW$
is also not invertible.
\end{proof}

>>>>

Let $\Omega$ be a bounded domain with $C^2$ boundary
denoted by $\Gamma$.
The Dirichlet problem specifies the
velocity of the fluid on the boundary, i.e.

@@

In the following lemma, we show that the oscillatory
Stokeslet satisfies the radiation condition. 
\begin{lem}
The oscillatory Stokeslet, as defined in \eqref{eq:ostokeslet}, 
satisfies the radiation condition in Definition \ref{def:radcond}.
\end{lem}
\begin{proof}
Consider the Stokeslet induced by an arbitrary charge
$k^2 \bpsi$ at the origin where $\psi \in \mathbb{C}^2$ 
is a constant. Let $r = |\xx|$,
$\bnu(\xx) = \xx/|\xx|$, and $\btau(\xx) = \bnu(\xx)^\perp$. We have

@@

\begin{equation}
\left | \nabla \left( \partial_{\tau_x} \left ( 
\nabla^\perp \left (H_0^{(1)} (kr) \right ) \cdot \bpsi  \right )
\right) \right | = 0 \; , \nonumber
\end{equation}
so that the Stokeslet satisfies the radiation condition.
\end{proof}
A consquence of the above lemma is that the oscillatory Stokes
single layer potential satisfies the radiation condition.
\begin{cor}
Suppose that $\Gamma$ is the boundary of a region $\Omega$
and is $C^{2}$. 
Suppose that $\bmu \in C(\Gamma)\times C(\Gamma)$, then
the oscillatory Stokes single layer potential $\bS[\bmu]$,
as defined in~\cref{eq:singlelayer}, satisfies the radition condition.
\end{cor}
Unfortunately, the stresslet, as defined in~\cref{eq:ostress}, 
does not necessarily satisfy the radiation condition.
The reason for failure is the logarithmic growth of 
the pressure at $\infty$.
However, this turns out to be a rank-one issue and 
the oscillatory Stokes double layer potential
does satisfy the radiation condition 
if the density satisfies an integral constraint.
The following lemma proves this result.

\begin{lem}
Suppose that $\Gamma$ is the boundary of a region $\Omega$
and is $C^{2}$. 
Suppose that $\bmu \in C(\Gamma) \times C(\Gamma)$ and satsifies
$\int_{\Gamma} \bmu \cdot \bnu dS = 0$, where
$\bnu$ dentoes the outward normal to the curve $\Gamma$.
Then, the oscillatory Stokes 
double layer potential $\bD[\bmu]$, as defined in \eqref{eq:doublelayer},
also satisfies the radiation condition.
\end{lem}

\begin{proof}
We only establish the
decay of the pressure, which we will denote by $p^\bD$;
the rest of the terms in \eqref{eq:radcond} can be bounded
using an argument like that for the Stokeslet above.
Because $p^\bD$ is harmonic in the exterior of any disc
containing $\Gamma$, it is sufficient to show that
$|\nabla p^\bD| = \bigo (1/r^2)$. Let $\btau$ denote the
positively oriented tangent to the curve $\Gamma$ and
$\mu_\nu(\yy)$ and $\mu_\tau(\yy)$ denote $\bmu(\yy) \cdot \bnu(\yy)$ and
$\bmu(\yy) \cdot \btau(\yy)$, respectively. Substituting
$\bD \bmu$ into \eqref{eq:ostokes}, we obtain

@@

@@

\begin{proof}
Since $\bu$ satisfies the radiation condition at $\infty$ and $\bt = i\eta \bu$
on $\Gamma$, it follows from~\cref{eq:repinfest} that
\begin{align*}
0 &=
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
dV \nonumber \\
& \qquad - 2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\bt} dS  \right) \\
&= 
\int_{|\by|=r} \left( |\bt|^2 + |k|^2 |\bu|^2 \right) dS +
2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |2\be(\bu)|^2 \right)
dV \nonumber \\
& \qquad + 2 \left( \left (\Re(k)\Re(\eta) + \Im(k)\Im(\eta)
\right ) \int_{\Gamma} |\bu|^{2} dS  \right)
\, .
\end{align*}
Because all of the quantities in the last expression above are
nonnegative, we have that
\begin{equation}
  \int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \, .
  \nonumber
\end{equation}
The result then follows from the uniqueness of solutions to the exterior
Dirichlet problem.
\end{proof}

@@

\subsubsection{Dirichlet eigenvalues --- double layer
  representation}
\label{subsec:dlanalysis}
Suppose that the solution to the oscillatory
Stokes Dirichlet problem, \cref{eq:dir_interior},
is represented using a double layer potential defined
on $\Gamma$, i.e. setting $\bu = \bD_{k} \bmu$ where
$\bmu$ is an unknown density. 
Substituting this expression
into the boundary condition and applying
\cref{lem:jump-conds}, we obtain

@@

On simply connected domains, there is a one-to-one correspondance between
the eigenvalues of the Dirichlet problem for
the Stokes equation
and the values of $k$ for which the operator $(\cI - 2\cD_{k} - 2\cW)$
is not invertible. To prove this, we also need the 
following lemma:
\begin{lem}
  \label{lem:nutracli}
  If $\bt^{-}$ is the surface traction associated
  with an interior Dirichlet Stokes eigenfunction $\bu$,
  then $\bt^{-}$ and $\bnu$ are linearly independent.
\end{lem}
\begin{proof}
We first note that $\bS_{k}[\bnu](\bx) = 0$ for all $\bx \in \Omega$.
This follows from the application of the divergence theorem and the fact that
oscillatory Stokeslet is divergence free in $\Omega$. 
If $\bt^{-}$ is a surface traction associated with a Stokes eigenvalue, then
using Green's theorem, it follows that
$\bS_{k}[\bt^{-}](\bx) = \bu(\bx) \neq 0$ for $\bx \in \Omega$ and
thus $\bt^{-}$ and $\bnu$ are linearly independent.
\end{proof}

\begin{thrm}
\label{thm:dlmain}
Suppose that $\Omega$ is a bounded, simply connected domain. Then, the operator
$(\cI - 2\cD_{k} - 2 \cW)$ is not invertible if and only if $k^2$ is a
Dirichlet eigenvalue for the Stokes equation on $\Omega$.
\end{thrm}
\begin{proof}
  Suppose that $k^2$ is not a Dirichlet eigenvalue for
  the Stokes equation on
$\Omega$. 
Suppose further that $\bmu$ satisfies
\begin{equation}
(\cI - 2\cD_{k} - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
\end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:dlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:dlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu]$ in $\Omega$.
Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
and applying~\cref{lem:jump-conds}, we get that the interior
limit of the velocity $\bu^{-}$, is given by $(\cI - 2\cD_{k}) \bmu = 0$
on $\Gamma$. Since $k^2$ is not a Dirichlet eigenvalue for the Stokes
equation on $\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
In particular, this implies that the interior limit of the surface traction
denoted by $\bt^{-} = 0$ on $\Gamma$. 
Using~\cref{lem:jump-conds} again, we conclude that the exterior limit
of the surface traction, $\bt^{+}$, is $0$ on $\Gamma$. 
Note that $\bu$ is a radiating solution of the oscillatory
Stokes equation in the exterior $E$, as $\cW[\bmu] = 0$ implies
$\int_{\Gamma} \bmu \cdot \bnu = 0$.
From the uniqueness of the Neumann problem in the
exterior $E$, we conclude that $\bu \equiv 0$ in $E$ as well,
which in particular implies that
the exterior limit of the velocity, $\bu^{+}$, is $0$ on $\Gamma$.   
Using the jump conditions in~\cref{lem:jump-conds} again, we
get that $\bmu = \bu^{-} - \bu^{+} = 0$.
Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k^2$
is not a Dirichlet eigenvalue for the Stokes equation on $\Omega$.

@@

\begin{proof}
  Suppose that $k^2$ is not a Dirichlet eigenvalue for the
  Stokes equation on $\Omega$. Suppose further that $\bmu$ satisfies
  \begin{equation}
    (\cI - 2\cD_{k} -2i\eta\cS_{k} - 2\cW) \bmu = 0 \, ,
    \label{eq:mlproofrep}
  \end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2i\eta \cS_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:mlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2i\eta\cS_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:mlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k} - 2i\eta \cS_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu] -2i\eta\bS_{k}[\bmu]$
in $\Omega$. Then $\bu$ is a solution to the oscillatory
Stokes equation in $\Omega$, and applying~\cref{lem:jump-conds},
we get that the interior limit of the velocity
$\bu^{-} = (\cI - 2\cD_{k} -2i\eta\cS_{k}) \bmu = 0$ on $\Gamma$.
Since $k^2$ is not a Dirichlet eigenvalue for the Stokes equation
on $\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
This in particular implies that the interior limit of the
surface traction, denoted by $\bt^{-}$, is $0$ on $\Gamma$.
Using~\cref{lem:jump-conds} we observe that $\bt^{+}
= -i\eta \bmu(\xx)$ and $\bu^{+} = -\bmu(\xx)$ on $\Gamma$, i.e.
$\bt^{+}=i\eta u^{+}$ and $u^{+}$ satisfies the homogeneous
exterior impedence problem.
\begin{remark}
  Note that there is potential for confusion here
  in that the exterior limit with respect to $\Omega$ 
  for the boundary $\Gamma_{j}$ is the traditional interior 
  limit with respect to the obstacle region $\Omega_{j}$.
\end{remark}
We first show that $\bmu=0$ on $\Gamma_{0}$. 
To this end, note that $\bu$ is a radiating solution
of the oscillatory Stokes equation in the exterior $E$,
since $\cW[\bmu] = 0$ implies that $\int_{\Gamma} \bmu
\cdot \bnu = 0$. From the uniqueness of the impedance problem
in the exterior $E_0$ of $\Omega_0$, we conclude that
$\bu \equiv 0$ in $E_0$ as well, which in particular
implies that $\bu^{+}=0$ on $\Gamma_{0}$.   
Using the jump conditions in~\cref{lem:jump-conds}
again, we get that
$\bmu = \bu^{-} - \bu^{+} = 0$ on
$\Gamma_{0}$. To show that $\bmu=0$ on
$\Gamma_{j}$, we observe that $\bu$ is also a
solution to the oscillatory Stokes equation in each
of the obstacles $\Omega_{j}$.
Applying the energy-type identity \cref{eq:greenlike}
and using the fact that 
the interior limits with respect to $\Omega_{j}$
of the surface traction and the velocity
are $i\eta \bmu$ and $\bmu$ respectively, we get
\begin{equation}
\int_{\Omega_{j}} (|\be(\bu)|^{2} - \overline{k}^{2} |\bu|^2) dV 
= \int_{\Gamma_{j}} \bu \cdot \overline{\bt} dS = 
i\overline{\eta}\int_{\Gamma_{j}} |\bmu|^2 dS \, .
\end{equation}
Taking the imaginary part of the above equation,
we get
\begin{equation}
2 \text{Re}(k) \text{Im}(k) \int_{\Omega_{j}} |\bu|^2 + \text{Re}(\eta)
\int_{\Gamma_{j}} |\bmu|^2 dS = 0 \, .
\end{equation}
Since $\text{Re}(\eta)>0$, this implies that
$\bmu=0$ for $\xx \in \Gamma_{j}$, $j=1,2,\ldots m$. 
Thus, $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is
invertible when $k^2$ is not a Dirichlet eigenvalue
for the Stokes equation on $\Omega$.

From \cref{thrm:rep-theorem}, we have 
\begin{equation} \label{eq:rep-theorem}
  \bS [\bt](\xx) - \bD[\bu](\xx) = \begin{cases} 
    \bu(\xx) &\quad \xx \in \Omega \, , \\
    0 &\quad \xx \in \Omega^{C} \; .
    \end{cases}
  \end{equation}
Suppose that $k^2$ is Dirichlet eigenvalue for
the Stokes equation on $\Omega$ and let $\bu$
denote the corresponding eigenfunction and $\bt$ denote
its surface traction. Note that \cref{thrm:rep-theorem}
implies that $\cS_{k}[\bt^{-}] = 0$, since
$\bu^{-}=0$ on $\Gamma$. Applying \cref{thrm:rep-theorem}
to the pair $\bt^{-}, \bu^{-}$ and evaluating the
traction on $\Gamma$ using~\cref{lem:jump-conds},
we get
\begin{equation}
\bt^{-} = (\cDt_{k} + \frac{1}{2} \cI) \bt^{-} \, . 
\end{equation}
Combining these two identities, we get
that
\begin{equation}
(\cI - 2\cDkt -2i\eta \cS_{k}) \bt^{-} = 0 \, .
\end{equation}
As in the proof of~\cref{thm:dlmain}, letting
$c = \left< \bt^{-} ,\bnu \right>$, it follows that
\begin{equation}
  (\cI - 2\cDkt - 2i \eta \cS_{k} - 2\cW)
  (\bt^{-} - c\bnu) = 0 \, ,
\end{equation}
where $\bt^{-} - c\bnu \neq 0$.
Since $\bt^{-} - c\bnu$ is non-trivial and both
$i\eta \cS_{k}$ and $\cW$ are self-adjoint with respect
to the bilinear form \cref{eq:bi_form},
it follows from the Fredholm alternative
that the operator $\cI - 2\cDk -2i\eta \cSk - 2\cW$
is also not invertible.
\end{proof}
